\problemname{Meow Factor 2}

\illustration{0.45}{cat}{\href{https://www.flickr.com/photos/stefantell/354864230/in/photostream/}{Picture} by Stefan Tell on Flickr, cc by}%
\noindent
Strings of yarn have been popular in Catland for ages.  Which cat has
not spent many a lazy afternoon bouncing around a ball of yarn?
Lately however, strings of yarn have gotten competition: strings of
characters.  It turns out that these are almost as much fun as yarn,
and generally much safer as well (so far, no cat has had to call 911
on account of any character string-related entanglement accidents).

Naturally, some strings are more stylish than others, and for cool
cats it is important to engage in their string-playing pastime with
style.  The \emph{meow factor} of a string $S$ is the minimum number
of operations needed to transform $S$ into a string $S'$ which
contains the word ``meow'' as a substring, where an operation is one
of the following four:
\begin{enumerate}
\item Insert an arbitrary character anywhere into the string.
\item Delete an arbitrary character anywhere from the string.
\item Replace any character in the string by an arbitrary character.
\item Swap any two adjacent characters in the string.
\end{enumerate}
Write a program to compute the meow factor of a string of characters.

\section*{Input}

The input consists of a single line containing a string $S$,
consisting only of lower-case letters `\texttt{a}'-`\texttt{z}'.  The
length of $S$ is at least $1$ and at most $10^6$.

\section*{Output}

Output the meow factor of $S$.

